Distributed Multi-Heuristic A* (HAMSTAR)

### 2014-12-15 paper.tex
abstract is no longer the same size as everything else
some cleanup, but for some reason the prints in graphfile2.m stopped working

\documentclass[11pt]{article}

@@

\abstract{A* is a popular graph search algorithm used in many artificial intelligence applications. The original A* algorithm uses a single heuristic to prioritize exploration through a graph, but a variation on the algorithm known as shared multi-heuristic A* (SMHA*) makes use of multiple heuristics to more quickly arrive at near-optimal solutions. For this project, we implemented a distributed version of SMHA*, separating each heuristic into a separate process. We compare the results of our distributed implementation to the original SMHA* algorithm. In particular, we provide evidence that in domains where state expansions are expensive, our distributed approach may outperform SMHA*.

@@

\begin{figure}
\centering \includegraphics[width=5.0in]{system-diagram}
\caption{A diagram of our system. One machine starts up the others and runs the monotone anchor search. The other machines run their individual heuristics. Communication is done using MPI. 
\textcircled{1}\textbf{Anchor:} Starts heuristic machines; performs state expansions using anchor heuristic; receives, resolves, and broadcasts table updates; checks for termination conditions. \textcircled{2}\textbf{Heuristic:} Expands a likely state (chosen using heuristic); updates path cost to its successors; communicates updates to anchor; checks for termination conditions}
\label{fig:sysdiag}
\end{figure}

@@

\begin{figure}
\centering
\begin{subfigure}{3in}
  \includegraphics[width=3in]{pseudocode}
  \caption{Pseudocode}
  \label{fig1}
\end{subfigure}
\begin{subfigure}{2in}
  \includegraphics[width=2in]{graphs/puzzle}
  \caption{15-puzzle goal configuration}
  \label{fig2}
\end{subfigure}
\caption{Pseudocode from Aine et al., detailing the original sequential version of the algorithm we parallelized, alongside the sliding tile puzzle which we use it to solve.}
\label{fig:pseudocode}
\end{figure}

@@

SMHA* specifies two weight parameters. The first weight ($w_1$) gives the search a more depth-first goal-directed focus. The second weight ($w_2$) determines the margin by which a proposed solution's cost may exceed the anchor's minimum frontier key value, which is itself $w1$ times a lower bound on the optimum solution cost. Therefore, SMHA* guarantees that the solution found at termination is at most $w_1 w_2$ times the optimum value. This guarantee applies equally well in our distributed variant. For all experiments, we used $w_1 = w_2 = 2$. Every state expanded by the anchor has a $g$ value which is optimal to within a factor of $w_1$.

@@

\begin{figure}[b]
\centering
\includegraphics[width=0.4in]{graphs/hamstar}
\end{figure}

>>>>

\documentclass{article}

@@

\begin{abstract}
A* is a popular graph search algorithm used in many artificial intelligence applications. The original A* algorithm uses a single heuristic to prioritize exploration through a graph, but a variation on the algorithm known as shared multi-heuristic A* (SMHA*) makes use of multiple heuristics to more quickly arrive at near-optimal solutions. For this project, we implemented a distributed version of SMHA*, separating each heuristic into a separate process. We compare the results of our distributed implementation to the original SMHA* algorithm. In particular, we provide evidence that in domains where state expansions are expensive, our distributed approach may outperform SMHA*.
\end{abstract}

@@

\begin{figure}[h]
\centering \includegraphics[width=5.0in]{graphs/system-diagram}
\caption{A diagram of our system. One machine starts up the others and runs the monotone anchor search. The other machines run their individual heuristics. Communication is done using MPI. 
\textcircled{1}\textbf{Anchor:} Starts heuristic machines; performs state expansions using anchor heuristic; receives, resolves, and broadcasts table updates; checks for termination conditions. \textcircled{2}\textbf{Heuristic:} Expands a likely state (chosen using heuristic); updates path cost to its successors; communicates updates to anchor; checks for termination conditions}
\label{fig:sysdiag}
\end{figure}

@@

\begin{figure}[h]
\centering
\begin{subfigure}{3in}
  \includegraphics[width=3in]{graphs/pseudocode}
  \caption{Pseudocode}
  \label{fig1}
\end{subfigure}
\begin{subfigure}{2in}
  \includegraphics[width=2in]{graphs/puzzle}
  \caption{15-puzzle goal configuration}
  \label{fig2}
\end{subfigure}
\caption{Pseudocode from Aine et al., detailing the original sequential version of the algorithm we parallelized, alongside the sliding tile puzzle which we use it to solve.}
\label{fig:pseudocode}
\end{figure}

@@

SMHA* specifies two weight parameters. The first weight ($w_1$) gives the search a more depth-first goal-directed focus. The second weight ($w_2$) determines the margin by which a proposed solution's cost may exceed the anchor's minimum frontier key value, which is itself $w_1$ times a lower bound on the optimum solution cost. Therefore, SMHA* guarantees that the solution found at termination is at most $w_1 w_2$ times the optimum value. This guarantee applies equally well in our distributed variant. For all experiments, we used $w_1 = w_2 = 2$. Every state expanded by the anchor has a $g$ value which is optimal to within a factor of $w_1$.

@@

\begin{figure}[b]
\centering
\includegraphics[width=0.49in]{graphs/hamstar}
\end{figure}
